Kronos \& Krios: Evidence for accretion of a massive, rocky planetary system in a comoving pair of solar-type stars

### 2017-11-21 paper/ms.tex
Tidy up for circulation

While the data described above strongly suggests that the two stars are coeval,
this subsection explores the possibility that this pair is still not a
primordial binary.
Two stars unrelated at birth may end up in a binary system via a binary-single
scattering event that results in an exchange of binary members.
In order to estimate the rate at which any binary-single
event will produce a wide binary system such as \sunanalog\ and \bizarreone,
we may consider the rate at which this wide binary will scatter with a field star to
result in an exchange reaction.
The cross-section of exchange scattering for a binary with semi-major axis $a$ is
\begin{eqnarray}
  \sigma_\mathrm{ex} = \frac{640}{81} \pi a^{2} \left(\frac{v_i}{v_c}\right)^{-6}
  \label{eq:crosssection}
\end{eqnarray}
where $v_i$ is the incoming velocity, and $v_c$ is the critical velocity,
defined as
\begin{eqnarray}
  v_c^2 = G \frac{m_1 m_2 (m_1 + m_2 + m_3)}{m_3 (m_1 + m_2)} \frac{1}{a}\,\,.
\end{eqnarray}
\eqname~\ref{eq:crosssection} is appropriate when $v_i/v_c \gg 1$
(\citealt{Hut:1983aa,Hut:1983ab}), which is the case for wide binaries
scattering with field (disk) stars.
If we assume that field stars are made of solar-mass stars with a constant
number density $n=1$~pc$^{-3}$, and the incoming velocity of field stars is
$10$~km\,s$^{-1}$, the rate of exchange scattering is
\begin{eqnarray}
  n \sigma_\mathrm{ex} v_i = 6.82\times 10^{-8}\,\mathrm{Gyr}^{-1}
  \frac{n}{\mathrm{pc}^{-3}} \frac{\mathrm{pc}}{a}
  \left(\frac{10~\mathrm{km}\,\mathrm{s}^{-1}}{v_i}\right)^5\,,
\end{eqnarray}
low enough to be negligible.

>>>>

Another possibility that two stars unrelated at birth may end up in a binary
system is via a binary-single scattering event that results in an exchange of
binary members.
In order to estimate the rate at which any binary-single
event will produce a wide binary system such as \sunanalog\ and \bizarreone,
we may consider the rate at which this wide binary will scatter with a field star to
result in an exchange reaction.
The cross-section of exchange scattering for a binary with semi-major axis $a$ is
\begin{eqnarray}
  \sigma_\mathrm{ex} = \frac{640}{81} \pi a^{2} \left(\frac{v_i}{v_c}\right)^{-6}
  \label{eq:crosssection}
\end{eqnarray}
where $v_i$ is the incoming velocity, and $v_c$ is the critical velocity,
defined as
\begin{eqnarray}
  v_c^2 = G \frac{m_1 m_2 (m_1 + m_2 + m_3)}{m_3 (m_1 + m_2)} \frac{1}{a}\,\,.
\end{eqnarray}
\eqname~\ref{eq:crosssection} is appropriate when $v_i/v_c \gg 1$
(\citealt{Hut:1983aa,Hut:1983ab}), which is the case for wide binaries
scattering with field (disk) stars.
If we assume that field stars are made of solar-mass stars with a constant
number density $n=1$~pc$^{-3}$, and the incoming velocity of field stars is
$10$~km\,s$^{-1}$, the rate of exchange scattering is
\begin{eqnarray}
  n \sigma_\mathrm{ex} v_i = 6.82\times 10^{-8}\,\mathrm{Gyr}^{-1}
  \frac{n}{\mathrm{pc}^{-3}} \frac{\mathrm{pc}}{a}
  \left(\frac{10~\mathrm{km}\,\mathrm{s}^{-1}}{v_i}\right)^5\,,
\end{eqnarray}
low enough to be negligible.
